---
title: "Guide to using binomial"
author: "Grant Kalasky"
date: "5/1/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to cointoss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial: An Introduction

This package, `binomial`, is meant to provide functions that can be used 
to calculate the  probabilities of a Binomial random variable. The package
also includes other related functions including the probability
distribution, variance, expected value, and more!


## Bin Variable

With this package, you can create a binomial variable using the 
`bin_variable` function. 

```{r}
binvar1 <- bin_variable(5, 0.2)
binvar1
```

It returns a list with named elements:
- `trials`: the number of trials
- `prob`: probability of success

This list is a `binvar` binomial object. With this object, we can get a 
full summary description of the `binvar` object using the `summary()` 
function. It returns a list with the following named elements:
– `trials`: number of trials
– `prob`: probability of success
– `mean`: mean or expected value
– `variance`: variance
– `mode`: mode
– `skewness`: skewness
– `kurtosis`: kurtosis

```{r}
summary(binvar1)
```


## Functions of measures

The package also contains functions to calculate the numbers mentioned
above in the `summary()` of a `binvar` binomial object. Below, we show 
you how to invoke these functions to get these calculations:

```{r}
bin_mean(10, 0.3)

bin_variance(10, 0.3)

bin_mode(10, 0.3)

bin_skewness(10, 0.3)

bin_kurtosis(10, 0.3)

```


## Bin Choose

This function calculates the number of combinations in which `k` successes
can occur within `n` trials. You can invoke this function with `bin_choose`. 
It takes two arguments, `n` which are the number of trials and `k` which 
is the number of successes. 

```{r}
bin_choose(n = 5 , k = 2)
bin_choose(4, 2)
```


## Bin Probability

This function calculates the probability of a Binomial random variable,
given the number of successes, trials, and probability of success. 

```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```


## Bin Distribution

This function, like `bin_probability`, calculates the probabilities of a
Binomial random variable given the number of trials and probability of success. 
However, this function outputs multiple probabilities given the number of 
successes, from 0 successes to the inputed number of trials. 

The output is a dataframe with a class `bindis`.

```{r}
bin_distribution(trials = 5, prob = 0.5)
```


## Bin Cumulative

Similar to `bin_distribution`, the function `bin_cumulative()` outputs
a dataframe with the probabilities of a Binomial random variable, but 
includes the cumulative probability in addition to the probability 
distribution of the Binomial random variable. 

The output is a dataframe with a class `bincum`.

```{r}
bin_cumulative(trials = 5, prob = 0.5)
```


## Plotting `bindis` and `bincum` Objects

You can use the function `plot()` to graph a `bindis` binomial 
object. It returns a barplot that displays the probability histogram 
of the `bindis` object. 

```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

Similarly, you can also use the same function `plot()` to graph a 
`bincum` binomial object. It returns a linegraph of the cumulative
distribution of the `bincum` object. 

```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```


